On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2015-09-02 MS.tex
Change in text
clean brackets

\title{Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted}

\author[1]{Anais Gibert*}
\author[1]{Emma F. Gray}
\author[1]{Mark Westoby}
\author[1]{Ian J. Wright}
\author[1]{Daniel S. Falster}
\affil[1]{Dept of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia}

@@

\textit{Running title (36/45 characters)} Trait influence on growth along plant size

\textit{Corresponding author} Anais Gibert, anais.gibert@gmail.com, Dept of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia, tel: +61 2 9850 8194

@@

\section*{Introduction}\label{introduction}
Plant "ecological strategy" refers to how species face the challenge they all share: to acquire sufficient water, nutrients and light to live long enough to replace themselves with offspring. Growth rates have often been seen as central elements of plant ecological strategies. An idea that species strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions. Seedling potential relative growth rate (RGR) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) classification (e.g. \citealt{grime1979plant, Grime:1997wm}). Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}. From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}. An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species. Since then, traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.

Currently, two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates. The 'leaf economic spectrum' \citep{Wright:2004jb} and the 'wood economic spectrum' \citep{Chave:2009iy} reflect tissue construction costs (for specific leaf area and for wood volume respectively) trading off with tissue turnover rates or mortality risks. It has been widely expected that species with low tissue construction cost will typically have fast growth rates at least in favourable physical environments (e.g. \citealt{MullerLandau:2004dc,Wright:2004jb,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}). Yet, a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that. Consider SLA as an illustration. Species with high SLA can deploy more canopy area for a given dry mass investment in leaves \citep{Poorter:1999wd, Reich:1992wm}. In addition, SLA is correlated with high photosynthetic rates and high nitrogen (N) or phosphorus concentrations in the leaf \citep{Wright:2004jb}. For seedling relative growth rates under favourable conditions, high SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}. Yet for adult plants, this correlation appears weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}. The growing discrepancy between theoretical expectation and empirical results has led some to question whether traits are even useful for understanding growth \citep{Wright:2010tp, Paine:2015df}.

Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Enquist:2007ek,Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}. Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}. At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighted by the high costs of rapid leaf turnover (see section "Theoretical expectations"). While recent empirical studies supported the idea of a variation in the relationships between traits and growth rates across plant sizes (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear. It is still an opening question whether the influence of traits on growth change with plant size in a predictable and consistent way.

In this paper, we used a meta-analytic approach on five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, maximum height= Hmax, and seed mass= SM) to investigate:
\begin{enumerate}
  \item How general is the tendency for correlations between traits and growth rate to vary with plant size?
  \item  Do the observed relationships conform to predictions (outlined in section "Theoretical expectations") from a recently developed mechanistic model (Falster et al., 2011; Falster, 2013)?
\end{enumerate}
We gathered correlation coefficients between trait and growth from studies that gave explicit information about the size or stage of the plants. While most studies on traits have not been concerned with effects of plant size, they have generally reported trait-growth correlations for identifiable stage classes. We used plant stage (i.e. juvenile, sapling and adult) as a first approximation of plant size. We focused mainly on tree and woody species since the mechanistic model used to assess our predictions is most applicable to tree.

@@

\subsection*{Literature snapshot}\label{literature-snapshot}
We aimed to identify studies that measured the correlation between five prominent functional trait (SLA, WD, Aarea, Hmax and Seed mass) and a growth measurement across species. According to a snapshot of the literature on Web of Science database (Thomson Reuters), 82\% of the literature for these 5 traits is captured by searching only on SLA and WD. This snapshot was performed between March and June 2014 using a range of Boolean search terms in English. Search terms were as follows: (''TRAIT'' AND (''growth rate'' OR ''relative growth rate'')) AND (''tree*'' OR ''woody*''), ''TRAIT'' was all trait names listed in Table A1. While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}. This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed. Thus, we used Google Scholar to perform a more systematic search of the literature for SLA and WD.

\subsection*{Systematic search}\label{systematic-search}
Google Scholar database was searched using the range of Boolean search terms for SLA and WD. Search terms were as follows: ((''SLA'' OR ''LMA'' OR ''specific leaf area'' OR ''leaf mass area'' OR ''wood density'' OR ''WD'' OR ''wood specific gravity'' OR ''stem density'' OR ''stem specific density'') AND (''growth rate'' OR ''relative growth rate'')) AND (tree* OR woody*). The keyword search in Google Scholar returns approx. 18900 papers. For comparison, with the same keyword search Web of Science returns 541 papers. Thus, in Google Scholar we displayed papers by relevance and examined the first 750 items. We also identified and recorded other possible data sources using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al). To avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a 'failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting a correlation coefficient value. The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.

@@

The authors of the 112 articles reported in our meta-analyses, categorized plants into four differents stages (i.e. seedling, juvenile, sapling, adult). While the stage categories have been established according to the expertise and the appreciation of the authors, by compiling data across multiple studies and across different growth form (tree and woody, etc), there is a risk of assigning plants of similar size to different categories. We verified the consistency of size/age range attributed to each stage across the 112 studies reported here. Fig. \ref{Fig2} showed that the thresholds in size/age used by the authors to defined a plant stage are quite steady. In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm). According to simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015}, these stage cutoffs match across the different size measurements (i.e. diameter, height and age, Fig. \ref{FigA1}). The size/stage threshold defined across the 112 articles, allowed us to attribute straightforwardly a stage category to studies for which no stage have been distinctly mentionned by the authors (5\% of the data, noted as 'mix' in Fig. \ref{Fig2}).

Less than 5\% of the studies (i.e. five studies on 112) were ambiguous on their plant stage attribution. Half of these equivocal cases involved the juvenile category. The term "juvenile" is vague enough to cover size range from either seedling or sapling stages. according to the authors. This redundancy encourages us to focus on a three stage classification (i.e. juvenile, sapling, adult) instead of a four stage one (i.e. seedling, juvenile, sapling, adult). In the rest of the mansucript we preferred the term "juvenile" to "seedling", because for a portion of the scientific community "seedling" also refers to a particular experimental condition (a greenhouse experiment). We attributed a study to a new stage category only when 95\% of the recorded range of sizes for that study lay within a new stage category. The others equivocal cases were caused by an ambiguity in the definition of "adult" used by the authors. Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive (see ID 52 and 50). Here, we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless the plant size or age. Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig. \ref{FigA5} model.1. In the main text, we report the results using the standardized categories.

@@

Sensitivity analysis:
We tested how robust are our results to the decision made in the analysis. In particular we tested our prediction using two datatset with different inclusion criteria. The number of species used to perform the correlation, the experimental conditions, and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses. Therefore, we focused exclusively on correlation across species, and we stratified the data set into two subsets: one including only studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset). We excluded from the 'ideal' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for seed mass (i.e. seed stage), or Hmax (i.e. adult stage). 
We also tested the sentivity of our results to the dominance of one or a few studies that measured a large number of response for the same trait. In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size. This corresponds to the ”reduced dataset” where multiple responses were condensed into a single average within a trait and within a study.

@@

\subsection*{Availability of code and data}\label{code}

All analyses were conducted with R software \citep{Ralanguageanden:2014wf}. The code and data underpinning this paper is available at github.com/AnaisGibert/Growth\_trait\_metaanalysis. Archival copies are also included in Appendix \ref{app:supp_info_files} in Supplementary material.

@@

Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results. The results reported were confined to correlations across species, and under non-stressed conditions (n=176). A "complete" dataset (n=216) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements. This "complete" dataset generated similar effect sizes to those reported above from the "ideal" dataset, and led to similar conclusions (Fig. \ref{Fig3} grey points). Differences concerned often the confidence intervals around particular mean effect sizes in Fig. \ref{Fig3}. These differences in CI were not easily attributed to any single cause. For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used wood density values from adult plants together with growth from juveniles. For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 7 correlations measured under low light conditions were added. Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig. \ref{FigA5}).

@@

Light and water micro-environments can affect growth values, and might modify correlations with traits in relation to plant size. For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes. Similarly, instead of a negative correlation between WD and growth across all plant stages, \citep{Iida:2014ep,Iida:2014hq} found a negative correlation at small size that disappeared when trees were larger. \citet{Iida:2014hq} explained the switch in directionality by changes in light and water condition up the vertical profile within a forest: larger trees reached a position in the canopy where they were released from light limitations, other resources such as water may have become limiting, and the performance of trees may then have been regulated by different traits. Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and WD occurred for trees larger than 22-26 cm dbh. This points to one of the possible limitations in our meta-analysis, where trees with height above 5 m were pooled as "adult".

@@

\begin{figure}[h!]
\centering
\includegraphics{output/Fig1.pdf}
\caption{Number of correlations between trait and growth for each plant stage recorded in our dataset. Shown here are 'raw dataset' (recorded both across and within species, under unstressed and stressed conditions). Bar colors: red for adult, orange for sapling, grey for juvenile. Aarea (or Amass) = rate of $CO_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax= asymptotic maximum height,  Ks =stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density}
\label{Fig1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/Fig2.pdf}
\caption{Range of plant size in \textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter and the plant stage assigned by the authors of the articles used in the meta-analyses. Each segment represents the plant size range (max and min values) of the species used to measure the correlation between growth and traits in each article. ID is the reference number of the article in our dataset. The colors represents the stage information given by the authors (green: seedling, blue: juvenile, orange: sapling, red: adult, grey: unspecified by the authors), the vertical line represents the most likely limits between stage categories, the horizontal line styles corresponds to the species growth form used in each study (solid line: exclusively tree, dashed line: woody species , dotted line: tree mixed with another growth form). Shown here are the "raw dataset" (recorded both across and within species, and under unstressed and stressed conditions).}
\label{Fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/Fig3.pdf}
\caption{The relationship between growth rates and SLA or seed mass changes with plant stage. Plots show the effect size (+ 95\%CI) of the correlation across species between growth rate and five functional traits for plant stage comparisons. \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Asymptotic height (Hmax) \textbf{d)} Seed mass and \textbf{e)} Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero. Shown here are 'across species dataset' (recorded only across species, and under both unstressed and stressed conditions). Black point: unstressed conditions, grey points: all the data. 'n' indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT, for unstressed conditions only) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means the stage model fitted the data better than the null model. 
}
\label{Fig3}
\end{figure}

@@

  1. Reporting full details of bibliographic searches & yes	& Google Scholar database was searched using the range of Boolean search terms ((''SLA'' OR ''LMA'' OR ''specific leaf area'' OR ''leaf    mass area'' OR ''wood density'' OR ''WD'' OR ''wood specific gravity'' OR ''stem density'' OR ''stem specific density'') AND (''growth rate'' OR ''relative growth rate'')) AND (tree* OR woody*), in english. & "Systematic search", Table A1 \\
  2. Reporting inclusion/exclusion criteria & yes & Studies included report i) correlation coefficient between growth and trait, ii) the sample size/ number of species, and iii) the size/stage of plants. Studies excluded report correlation within species	& "Systematic search" \\
  3. Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. The question addressed in our study concerns the correlation between growth and trait across species, thus the number of species is a better proxy of a study quality than sample size. &	 "Systematic search" and  "Effect size calculation" \\
 4. Specifying meta-analytical model &	yes	& Mixed-effect model with a study ID as a random variation, and stage as a fixed effect, m1 ~lmer (stage + (1|ID)) &	"Statistical analyses", Fig3 \\

@@

 7. Multifactorial analysis of explanatory variable	& yes & We focused on the "plant stage" as the main exploratory variable. Yet, the stage variable may be confunded with other explanatory moderators (i.e. growth measurement, experiment type or growth form). Thus, we checked if no one of them would not consistenly be a strongest predictor of the data. We did not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. & FigA4, FigA6  \\
  8. Testing for publication bias &	yes	& We used funnel plots for a visual assessement. We used the "trim and fill" method to estimate the number of studies missing (Duval and Tweedie 2000). We also estimated the Rosenberg’s fail-safe number (Rosenberg 2005). 	&  Appendix D, FigA7\\

>>>>

\title{On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted}

\author[1]{Anais Gibert*}
\author[1]{Emma F. Gray}
\author[1]{Mark Westoby}
\author[1]{Ian J. Wright}
\author[1]{Daniel S. Falster}
\affil[1]{Biological Sciences, Macquarie University NSW 2109, Australia}

@@

\textit{Running title (36/45 characters)}Influence of traits on growth changes with size

\textit{Corresponding author} Anais Gibert, anais.gibert@gmail.com, Biological Sciences, Macquarie University NSW 2109, Australia, tel: +61 2 9850 8194

@@

\section*{Introduction}\label{introduction}

The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients and light for growth, and then ultimately to replace themselves with offspring. An idea that species strategy differences might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions. Seedling potential relative growth rate (RGR) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) classification (e.g. \citealt{grime1979plant, Grime:1997wm}). Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}. From the 1990s a new style of ``trait ecology'' arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}. An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species. Since then, traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.

Currently, two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates. The ``leaf economic spectrum'' \citep{Wright:2004jb} and the ``wood economic spectrum'' \citep{Chave:2009iy} reflect tissue construction costs (for leaf area and for wood volume respectively), trading off with rates of tissue turnover or mortality. It has been widely expected that species with low tissue construction cost will typically have fast growth rates, at least in favourable physical environments \citep[e.g.][]{MullerLandau:2004dc,Wright:2004jb,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}. Yet, a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that. Consider SLA as an illustration. Species with high SLA can deploy more canopy area for a given dry mass investment in leaves \citep{Poorter:1999wd, Reich:1992wm}. In addition, SLA is correlated with high photosynthetic rates and high nitrogen (N) or phosphorus concentrations in the leaf \citep{Wright:2004jb}. For seedling relative growth rates under favourable conditions, high SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}. Yet for adult plants, this correlation appears weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}. The growing discrepancy between theoretical expectation and empirical results has led some to question whether traits are even useful for understanding growth \citep{Wright:2010tp, Paine:2015df}.

Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Enquist:2007ek,Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}. Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}. At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighted by the high costs of rapid leaf turnover (see section ``Theoretical expectations''). While recent empirical studies supported the idea of a variation in the relationships between traits and growth rates across plant sizes (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear. It is still an opening question whether the influence of traits on growth change with plant size in a predictable and consistent way.

In this paper, we used a meta-analytic approach on five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, maximum height= Hmax, and seed mass= SM) to investigate:
\begin{enumerate}
  \item How general is the tendency for correlations between traits and growth rate to vary with plant size?
  \item  Do the observed relationships conform to predictions (outlined in section ``Theoretical expectations'') from a recently developed mechanistic model (Falster et al., 2011; Falster, 2013)?
\end{enumerate}
We gathered correlation coefficients between trait and growth from studies that gave explicit information about the size or stage of the plants. While most studies on traits have not been concerned with effects of plant size, they have generally reported trait-growth correlations for identifiable stage classes. We used plant stage (i.e. juvenile, sapling and adult) as a first approximation of plant size. We focused mainly on tree and woody species since the mechanistic model used to assess our predictions is most applicable to tree.

@@

\subsection*{Literature snapshot}\label{literature-snapshot}
We aimed to identify studies that measured the correlation between five prominent functional trait (SLA, WD, Aarea, Hmax and Seed mass) and a growth measurement across species. According to a snapshot of the literature on Web of Science database (Thomson Reuters), 82\% of the literature for these 5 traits is captured by searching only on SLA and WD. This snapshot was performed between March and June 2014 using a range of Boolean search terms in English. Search terms were as follows: (``TRAIT'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), ``TRAIT'' was all trait names listed in Table A1. While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}. This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed. Thus, we used Google Scholar to perform a more systematic search of the literature for SLA and WD.

\subsection*{Systematic search}\label{systematic-search}
Google Scholar database was searched using the range of Boolean search terms for SLA and WD. Search terms were as follows: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (tree* OR woody*). The keyword search in Google Scholar returns approx. 18900 papers. For comparison, with the same keyword search Web of Science returns 541 papers. Thus, in Google Scholar we displayed papers by relevance and examined the first 750 items. We also identified and recorded other possible data sources using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al). To avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a ``failure to publish bias'' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting a correlation coefficient value. The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.

@@

The authors of the 112 articles reported in our meta-analyses, categorized plants into four differents stages (i.e. seedling, juvenile, sapling, adult). While the stage categories have been established according to the expertise and the appreciation of the authors, by compiling data across multiple studies and across different growth form (tree and woody, etc), there is a risk of assigning plants of similar size to different categories. We verified the consistency of size/age range attributed to each stage across the 112 studies reported here. Fig. \ref{Fig2} showed that the thresholds in size/age used by the authors to defined a plant stage are quite steady. In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm). According to simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015}, these stage cutoffs match across the different size measurements (i.e. diameter, height and age, Fig. \ref{FigA1}). The size/stage threshold defined across the 112 articles, allowed us to attribute straightforwardly a stage category to studies for which no stage have been distinctly mentionned by the authors (5\% of the data, noted as ``mix'' in Fig. \ref{Fig2}).

Less than 5\% of the studies (i.e. five studies on 112) were ambiguous on their plant stage attribution. Half of these equivocal cases involved the juvenile category. The term ``juvenile'' is vague enough to cover size range from either seedling or sapling stages. according to the authors. This redundancy encourages us to focus on a three stage classification (i.e. juvenile, sapling, adult) instead of a four stage one (i.e. seedling, juvenile, sapling, adult). In the rest of the mansucript we preferred the term ``juvenile'' to ``seedling'', because for a portion of the scientific community ``seedling'' also refers to a particular experimental condition (a greenhouse experiment). We attributed a study to a new stage category only when 95\% of the recorded range of sizes for that study lay within a new stage category. The others equivocal cases were caused by an ambiguity in the definition of ``adult'' used by the authors. Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive (see ID 52 and 50). Here, we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless the plant size or age. Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig. \ref{FigA5} model.1. In the main text, we report the results using the standardized categories.

@@

Sensitivity analysis:
We tested how robust are our results to the decision made in the analysis. In particular we tested our prediction using two datatset with different inclusion criteria. The number of species used to perform the correlation, the experimental conditions, and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses. Therefore, we focused exclusively on correlation across species, and we stratified the data set into two subsets: one including only studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset). We excluded from the ``ideal'' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for seed mass (i.e. seed stage), or Hmax (i.e. adult stage).
We also tested the sentivity of our results to the dominance of one or a few studies that measured a large number of response for the same trait. In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size. This corresponds to the ”reduced dataset” where multiple responses were condensed into a single average within a trait and within a study.

@@

Availability of code and data:
All analyses were conducted with R software \citep{Ralanguageanden:2014wf}. The code and data underpinning this paper is available at github.com/AnaisGibert/Growth\_trait\_metaanalysis. Archival copies are also included in Appendix \ref{app:supp_info_files} in Supplementary material.

@@

Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results. The results reported were confined to correlations across species, and under non-stressed conditions (n=176). A ``complete'' dataset (n=216) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements. This ``complete'' dataset generated similar effect sizes to those reported above from the ``ideal'' dataset, and led to similar conclusions (Fig. \ref{Fig3} grey points). Differences concerned often the confidence intervals around particular mean effect sizes in Fig. \ref{Fig3}. These differences in CI were not easily attributed to any single cause. For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used wood density values from adult plants together with growth from juveniles. For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 7 correlations measured under low light conditions were added. Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig. \ref{FigA5}).

@@

Light and water micro-environments can affect growth values, and might modify correlations with traits in relation to plant size. For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes. Similarly, instead of a negative correlation between WD and growth across all plant stages, \citep{Iida:2014ep,Iida:2014hq} found a negative correlation at small size that disappeared when trees were larger. \citet{Iida:2014hq} explained the switch in directionality by changes in light and water condition up the vertical profile within a forest: larger trees reached a position in the canopy where they were released from light limitations, other resources such as water may have become limiting, and the performance of trees may then have been regulated by different traits. Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and WD occurred for trees larger than 22-26 cm dbh. This points to one of the possible limitations in our meta-analysis, where trees with height above 5 m were pooled as ``adult''.

@@

\begin{figure}[h!]
\centering
\includegraphics{output/Fig1.pdf}
\caption{Number of correlations between trait and growth for each plant stage recorded in our dataset. Shown here are ``raw dataset'' (recorded both across and within species, under unstressed and stressed conditions). Bar colors: red for adult, orange for sapling, grey for juvenile. Aarea (or Amass) = rate of $CO_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax= asymptotic maximum height,  Ks =stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density}
\label{Fig1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/Fig2.pdf}
\caption{Range of plant size in \textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter and the plant stage assigned by the authors of the articles used in the meta-analyses. Each segment represents the plant size range (max and min values) of the species used to measure the correlation between growth and traits in each article. ID is the reference number of the article in our dataset. The colors represents the stage information given by the authors (green: seedling, blue: juvenile, orange: sapling, red: adult, grey: unspecified by the authors), the vertical line represents the most likely limits between stage categories, the horizontal line styles corresponds to the species growth form used in each study (solid line: exclusively tree, dashed line: woody species , dotted line: tree mixed with another growth form). Shown here are the ``raw dataset'' (recorded both across and within species, and under unstressed and stressed conditions).}
\label{Fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/Fig3.pdf}
\caption{The relationship between growth rates and SLA or seed mass changes with plant stage. Plots show the effect size (+ 95\%CI) of the correlation across species between growth rate and five functional traits for plant stage comparisons. \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Asymptotic height (Hmax) \textbf{d)} Seed mass and \textbf{e)} Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero. Shown here are ``across species dataset'' (recorded only across species, and under both unstressed and stressed conditions). Black point: unstressed conditions, grey points: all the data. ``n'' indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT, for unstressed conditions only) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means the stage model fitted the data better than the null model.
}
\label{Fig3}
\end{figure}

@@

  1. Reporting full details of bibliographic searches & yes	& Google Scholar database was searched using the range of Boolean search terms ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf    mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), in english. & ``Systematic search'', Table A1 \\
  2. Reporting inclusion/exclusion criteria & yes & Studies included report i) correlation coefficient between growth and trait, ii) the sample size/ number of species, and iii) the size/stage of plants. Studies excluded report correlation within species	& ``Systematic search'' \\
  3. Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. The question addressed in our study concerns the correlation between growth and trait across species, thus the number of species is a better proxy of a study quality than sample size. &	 ``Systematic search'' and  ``Effect size calculation'' \\
 4. Specifying meta-analytical model &	yes	& Mixed-effect model with a study ID as a random variation, and stage as a fixed effect, m1 ~lmer (stage + (1|ID)) &	``Statistical analyses'', Fig3 \\

@@

 7. Multifactorial analysis of explanatory variable	& yes & We focused on the ``plant stage'' as the main exploratory variable. Yet, the stage variable may be confounded with other explanatory moderators (i.e. growth measurement, experiment type or growth form). Thus, we checked if no one of them would not consistenly be a strongest predictor of the data. We did not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. & FigA4, FigA6  \\
  8. Testing for publication bias &	yes	& We used funnel plots for a visual assessment. We used the ``trim and fill'' method to estimate the number of studies missing (Duval and Tweedie 2000). We also estimated the Rosenberg’s fail-safe number (Rosenberg 2005). 	&  Appendix D, FigA7\\
  9. Sensitivity analysis &	yes &	We tested how robust are our results to the decision made in the analysis. We calculated effect size using 3 differents dataset: i) an  ``ideal'' dataset, focusing on unstressed conditions exclusively, ii) a ``complete dataset'' reporting all conditions, and iii) a ``reduced dataset'' where multiple responses were condensed into a single average within a trait and within a study. &	Fig3, FigA5 \\
